\documentclass[12pt]{article}
\usepackage{fullpage,enumitem,graphicx}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{amssymb,amsfonts,amssymb, amsthm}
\usepackage{mathtools}
\usepackage{fancyhdr}
\usepackage{physics}
\usepackage{textcomp}
\usepackage[table,x11names,svgnames]{xcolor}
\usepackage{soul}
\usepackage{parskip}
\usepackage{multirow}
\usepackage{array}
% \usepackage{chngcntr}
\usepackage{afterpage}
\usepackage{tabularx}
\usepackage{float}
\usepackage{placeins}
\usepackage{tablefootnote}
\usepackage{microtype}
\usepackage{subcaption}
\usepackage{verbatim}
\usepackage[letterpaper, portrait, margin=1.0in]{geometry}
\usepackage[linesnumbered, noline, noend]{algorithm2e}
\SetKw{Continue}{continue}
% \counterwithin{table}{section}
% \counterwithin{figure}{section}
\usepackage{mathtools}
\usepackage[thinc]{esdiff}

% Matrix related commands I collected
\newcommand*{\matr}[1]{\textbf{#1}}
\newcommand*{\tran}{^{\intercal}}
\newcommand*{\conj}[1]{\overline{#1}}
\newcommand*{\hermconj}{^{\textbf{H}}}
\newcommand*{\inv}{^{-1}}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

% Probability operators
\newcommand{\E}{\mathop{\mathbb{E}}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand*{\one} {\mathbf{1}}
\newcommand{\indicator}[1]{ \one \{ #1 \} }

% Graph
\newcommand*{\Pa}[1]{\textbf{Pa}(#1)}
\newcommand*{\Ch}[1]{\textbf{Ch}(#1)}
\newcommand*{\Nb}[1]{\textbf{Nb}(#1)}
\newcommand{\Sigmoid}{\mathrm{sigmoid}}

% optimization
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

%Define source code style
\usepackage{listings}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

\graphicspath{{.}}


\begin{document}

\begin{center}
{\Large CS221 Spring 2019 Poster session peer review}

\begin{tabular}{rl}
SUNet ID: & albertpl \\
Name: & Albert Liu \\
\end{tabular}
\end{center}

\begin{itemize}
  \item  Agar.AI Reinforcement Learning

   They use DQN to play Agar.io online game. They are able to analyze and iterate on their feature design. I think they know DQN and experience replay relatively well.

\item
  Deep RL with Experience Replay Trading Agent

  They formulate crypto currency trading as a RL problem and apply DQN. The network architecture is 3 layer LSTM and the features are derived features from raw close price, SMA/RSI/etc. I find the way they formulate the problem very interesting.


\item
  Alphalone: AI Agent for Abalone

  They analyzed the problem well and considered various approaches, minimax search, depth limited alphabeta pruning, move reorder, heuristics for evaluation function. Then settle on TD learning. I like the way they compare different approaches.



\end{itemize}

\end{document}
